NumPy---Array Programming in Python

### 2020-01-26 body.tex
Fix typo

The brevity and expressive power of NumPy's array programming syntax combined with 
an advanced interactive environment like IPython \cite{perez2007ipython}
or Jupyter \cite{Kluyver:2016aa} makes interactive data exploration fluid and simple.
It is common for NumPy users to work interactively with their data,
discovering through experimentation bits of code that they stich together into
imperative or functional programs.
The scientific Python ecosystem (Fig.~\ref{fig:ecosystem}) builds on top of
this solid foundation with core (e.g., SciPy and Matplotlib) libraries,
widely used technique-specific
libraries\cite{pedregosa2011scikit,vanderwalt2014scikit,SciPyProceedings_11},
and several domain-specific projects and libraries
\cite{astropy:2013,astropy:2018,cock2009biopython,millman2007analysis,2018EGUGA..2012146H}.
Exposing these simple array programming primitives, as well as the surrounding ecosystem of
tools, in Python---an interpreted, general purpose language---creates an ideal environment for
interactive, exploratory data analysis where users may iteratively inspect,
manipulate, and visualize their data.
This rich environment has made the scientific Python ecosystem popular for scientific
research.

>>>>

The brevity and expressive power of NumPy's array programming syntax combined with 
an advanced interactive environment like IPython \cite{perez2007ipython}
or Jupyter \cite{Kluyver:2016aa} makes interactive data exploration fluid and simple.
It is common for NumPy users to work interactively with their data,
discovering through experimentation bits of code that they stitch together into
imperative or functional programs.
The scientific Python ecosystem (Fig.~\ref{fig:ecosystem}) builds on top of
this solid foundation with core (e.g., SciPy and Matplotlib) libraries,
widely used technique-specific
libraries\cite{pedregosa2011scikit,vanderwalt2014scikit,SciPyProceedings_11},
and several domain-specific projects and libraries
\cite{astropy:2013,astropy:2018,cock2009biopython,millman2007analysis,2018EGUGA..2012146H}.
Exposing these simple array programming primitives, as well as the surrounding ecosystem of
tools, in Python---an interpreted, general purpose language---creates an ideal environment for
interactive, exploratory data analysis where users may iteratively inspect,
manipulate, and visualize their data.
This rich environment has made the scientific Python ecosystem popular for scientific
research.
